%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Publications}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------

\begin{cvpubs}

\vspace{-1mm}

\cvsubsection{Journal Articles}

  \pubentry
    {Burr S., Auckland K., Glynos A.* \textbf{Dhawanjewar A.S.*}, Wei W., Ryall C., Hynes-Allen A.M., Prater M., Sczaniecka-Clift M., Prudent J., Chinnery P.F., \& van den Ameele J. (2025).}
    {MitoPerturb-Seq identifies common and gene-specific single-cell responses to mitochondrial DNA depletion and heteroplasmy}
    {\textit{(Under Review)}}

  \pubentry
    {Chandrasegaram R., Hynes-Allen A.M., Gao B., \textbf{Dhawanjewar A.S.}, Frison M., Petridi S., Chinnery P.F., Ma H. \& van den Ameele J.(2025).}
  {Single-molecule mitochondrial DNA imaging reveals heteroplasmy dynamics shaped by developmental bottlenecks and selection in different organs in vivo}
  {\href{https://doi.org/10.1101/2025.01.24.634671}{bioRxiv, 2025.01.24.634671v1}}

  \pubentry
    {\textbf{Dhawanjewar, A.S.}, Montooth K.L., \& Meiklejohn, C.D.}
  {Mitochondrial OXPHOS genes exhibit higher levels of molecular compensation of human disease associated mutations relative to nuclear OXPHOS genes in mammals.}
  {\textit{In preparation, manuscript available on request}}

  \pubentry
    {M. Florencia Camus \& \textbf{Dhawanjewar, A.S.} (2023).}
  {Multilevel selection on mitochondrial genomes.}
  {\href{https://doi.org/10.1016/j.gde.2023.102050}{Current Opinion in Genetics \& Development, 80, 102050.}}

  \pubentry
    {\textbf{Dhawanjewar A.S.*}, Roy A.A.*, \& Madhusudhan M.S. (2020).}
	{A knowledge-based scoring function to assess the stability of quaternary protein assemblies.}
	{\href{https://doi.org/10.1101/562520}{Oxford Bioinformatics, 36(12), 3739-3748.}}

  \pubentry
     {Roy, A.A.*, \textbf{Dhawanjewar, A.S.*}, Sharma, P., Singh, G., \& Madhusudhan, M.S. (2019).}
  	{Protein Interaction Z Score Assessment (PIZSA): an empirical scoring scheme for evaluation of protein-protein interactions.}
	{\href{https://doi.org/10.1093/nar/gkz368}{Nucleic acids research, 47(W1), W331-W337.}}

  \pubentry
    {Montooth, K.L., \textbf{Dhawanjewar, A.S.}, \& Meiklejohn, C.D. (2019).}
	{Temperature-sensitive reproduction and the physiological and evolutionary potential for Mother's Curse.}	{\href{https://doi.org/10.1093/icb/icz091}{Integrative and comparative biology, 59(4), 890-899.}}

  \pubentry
    {Nelson, T.C., Jones, M.R., Velotta, J.P., \textbf{Dhawanjewar, A.S.}, \& Schweizer, R.M. (2019).}
	{UNVEILing connections between genotype, phenotype, and fitness in natural populations.}
	{\href{https://doi.org/10.1111/mec.15067}{Molecular ecology, 28(8), 1866-1876.}}

	\fontsize{10pt}{1em}\bodyfontlight\itshape\color{graytext} * Equal contribution

\end{cvpubs}

\vspace{2mm}

\cvsubsection{Web-servers}

\pubauthorstyle{Prediction of Stable Quaternary Protein Assemblies -} \\
\pubjournalstyle{\normalfont{PIZSA (Protein Interaction Z-score Assessment) - \href{http://cospi.iiserpune.ac.in/pizsa/}{http://cospi.iiserpune.ac.in/pizsa/}}}


